Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:07	12:31:14	(Mon 7.Sep)

The ultimate goal of adaptive beamformers is to take the information available in the wavefield and use it to either improve image resolution, noise suppression, or both. This non-linear processing increases the image bandwidth and hence introduces a to oversample it to capture all the details. For MVDR a factor 10 oversampling laterally compared to the Nyquist rate is often needed to ensure  spatially local shift-invariance in source amplitude~\cite{Asen2014}. Since LCA operates with the same optimization criterion, we will be using approximately a factor 8 lateral oversampling for both beamformers.

@@

% \section{Experimental Setup}
% 
% For the LCA to perform well it is important to let it have a diverse selection of windows to choose from. The question is how this selection should be With our ovarall goal being a reduction of computational complexity, it The choice of window function does not seem to matter. 
% 
% 
% 
% Using Kaiser windows as their extremal values areLimit our study to Kaiser windows
% 
% 
% 
% This selection is based on observations of the solutions found by the MV beamformer. We obtained good results in our experiments by letting the LCA beamformer select among 5 Kaiser windows with uniformly distributed $\beta$'s in the range $[0.05, 0.5]$ and a rectangular window. Each window was steered in 5 different directions, uniformly distributed within 80\% of the mainlobe width of the rectangular window, which is the most narrow. This adds to a total of 30 windows.
% 
% To make the choice of window less susceptible to pixel value uncertainties, the LCA beamformer was set to apply the most frequently selected window in an 11 pixel range region to the center pixel in that region. In physical terms, this is a region of approximately 20\,cm. The MV beamformer estimated the covariance matrix as described in~\cite{syn07} by averaging over 16 subarrays and 11 range pixels, and applying 3\% diagonal loading.

@@

MVDR was run with a fairly aggressive yet stable set of parameters; subarray size $L=16$, temporal averaging of $K=1$, and $d=1\%$ diagonal loading. Temporal averaging of $K=1$ was also used with LCA.

The results and the order they will be presented is as follows:

The following sections with expand and discuss these results further.

@@

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with responses that resembles that of MVDR. We study this in \Fig{mvdr_selected_windows}, where an MVDR sectorscan image of the Holmengraa wreck is presented, along with the window responses MVDR chose in the shadow, speckle and highlight regions of this image.

@@

\subsection{Kaiser parameter $\beta$ and steering $\phi$}

@@

@@

What's wrong here?

\begin{itemize}
\item Oversampling tests. Both Holmengraa and cross.
\item Mosaic indicating the number of windows needed.
\item 
\end{itemize}

% \begin{table}[!b]\centering%\normalsize
% \begin{tabular}[c]{l r r r@{}  l}\hline
% \rowcolor{tabBlue} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf B$_\text{arith}$} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf B$_\text{mem}$} & \multicolumn{2}{>{\columncolor{tabBlue}}c}{\bf B$_\text{mem}$/B$_\text{arith}$} \\\hline
% Arithmetic & 1.03 Tflop/s & & &\\
% Global memory & & 36 Gfloats/s & \hspace{30pt} 1 &:30 \\
% Shared memory & & 257 Gfloats/s & 1 &:4 \\
% Registers & & $>$1.5 Tfloats/s & $>$3 &:2~\cite{Vasilyy}
% \end{tabular}
% \caption{Nvidia Quadro 6000: Memory throughput, $B_{\lowercase{\text{mem}}}$, compared to arithmetic throughput, $B_\text{arith}$.}\label{throughputs}
% \end{table}%

>>>>

The ultimate goal of adaptive beamformers is to take the information available in the wavefield and use it to either improve image resolution, noise suppression, or both. This non-linear processing increases the image bandwidth introduces a need for a sampling rate higher than the Nyquist rate. For MVDR a factor 10 oversampling laterally compared to the Nyquist rate is often needed to ensure  spatialhift-invariance in source amplitude~\cite{Asen2014}. Since LCA operates with the same optimization criterion, we will be using approximately a factor 8 lateral oversampling for both beamformers.

@@

% 
% This selection is based on observations of the solutions found by the MV beamformer. We obtained good results in our experiments by letting the LCA beamformer select among 5 Kaiser windows with uniformly distributed $\beta$'s in the range $[0.05, 0.5]$ and a rectangular window. Each window was steered in 5 different directions, uniformly distributed within 80\% of the mainlobe width of the rectangular window, which is the most narrow. This adds to a total of 30 windows.
% 
% To make the choice of window less susceptible to pixel value uncertainties, the LCA beamformer was set to apply the most frequently selected window in an 11 pixel range region to the center pixel in that region. In physical terms, this is a region of approximately 20\,cm. The MV beamformer estimated the covariance matrix as described in~\cite{syn07} by averaging over 16 subarrays and 11 range pixels, and applying 3\% diagonal loading.

@@

MVDR was run with a fairly aggressive yet stable set of parameters; subarray size $L=16$ and $d=1\%$ diagonal loading. Both MVDR and LCA was run with $K=1$ temporal averaging.

The results will be presented in the following order: In section \ref{lca_window_function} we discuss typical window responses computed by MVDR (\Fig{mvdr_selected_windows}), and hypothesize  that these can be mimicked by Kaiser windows. In section \ref{lca_kaiser_parameters} we investigate what sensible boundaries for the Kaiser parameter $\beta$ and window steering $\phi$ should be (\ref{oversampling_mosaic_bounds}).

@@

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with responses that resembles that of MVDR. The typical responses MVDR creates for shadow, speckle and highlight regions of a sectorscan Holmengraa image is shown in \Fig{mvdr_selected_windows}.

@@

\subsection{Kaiser parameter $\beta$ and steering $\phi$}\label{lca_kaiser_parameters}

@@

\subsection{Computational complexity}

@@
